%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Anthony L}{Pane}{ \urlstyle{same}\href{https://www.linkedin.com/in/paneanthony/}{linkedin.com/in/paneanthony}\\
\href{mailto:alpane19@gmail.com}{alpane19@gmail.com} | 631.566.8353
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Stony Brook University}
\descript{B.S. in Computer Science}
\location{May 2002 | Stony Brook, NY}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Soft Skills}
Teamwork \\
Leadership \\
Problem-solving \\
Communication \\
Attention to detail \\
Adaptability \\
Mentorship \\
\sectionsep

\subsection{Strategic}
Clean Code \\
Domain Driven Design (DDD) \\
API Design: REST/Hypermedia \\
Microservices/Architecture \\
Agile: Scrum/Kanban \\
User Story Writing/Decomposition \\
Continuous Integration/Deployment \\
Design Patterns \\
Test Driven Development (TDD) \\
Functional Programming \\
Extreme Programming (XP) \\
\sectionsep

\subsection{Programming/Tools}
\location{Proficient:}
Java \textbullet{} Spring \textbullet{} Hibernate \textbullet{} SQL \\
JavaScript \textbullet{} TypeScript \textbullet{} HTML \\ 
React/Redux \textbullet{} Groovy \textbullet{} Spock \\
JSON/HAL \textbullet{} Sonar \textbullet{} Jenkins \textbullet{} GIT \\
ActiveMQ \textbullet{} Gradle \textbullet{} Jest \\
\location{Familiar:}
CSS \textbullet{} Scala \textbullet{} NoSQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{UniFocus Awards} 
\begin{tabular}{rll}
2011	     & Growth and Learning\\
2009	     & Team Excellence\\
2008	     & Growth and Learning\\
2007     & Innovation  \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{UniFocus}
\descript{| Principal Application Architect }
\location{August 2006 - Present | Denver, CO}
Drive the ability to efficiently and expertly create robust and maintainable product for 7 teams/45 staff located in the US, India, and Croatia.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Facilitate professional development of engineering and continue evolving the culture into a growth-oriented mindset.
\item Liaison between application development and architecture to ensure product infrastructure development is properly prioritized, implemented and delivered.
\item Recommend, evaluate, and oversee the implementation of toolsets, processes, or other technologies that directly impact product development.
\item Work with teams to design/train/advise/code on major technical design processes and initiatives.
\item Liaison between development and security/devops teams to ensure code analysis is being performed and reacted to accordingly.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Recent Projects}
\runsubsection{Gratuity - Digital Tipping}
\descript{| Principal Application Architect}
\location{Java, Spring, React, SQL | Teams: India, US}
Provide a cashless option for hotel guests to tip employees in order to increase employee satisfaction and retention.  
\begin{tightemize}
\item Analyzed requirements to create context map and visualize integration points using Domain Driven Design techniques resulting in two new bounded contexts.
\item Review UX designs to determine technical requirements and flow.
\item Design system to integrate with existing Tip Pooling features as well as future planned 'direct to employee' and 'bill to guest folio' options.
\item Negotiate, compromise, and prioritize initial feature set to ensure delivery of working product for demo and pilot phases.
\item Review and select payment processing solutions.  Review and select integration options to reduce PCI compliance risk.
\item Work with architecture and platform team to establish infrastructure, security, and delivery pipeline requirements.
\item Pair program and review code for defects and standards.
\end{tightemize}
\sectionsep

\runsubsection{Sonar OWASP Mitigation}
\descript{| Principal Application Architect}
\location{Java, Sonar, Gradle | Teams: US, India, Croatia, Architecture}
Use static code analysis tools to target known OWASP vulnerabilities across all projects leading to a 90\% reduction in targeted vulnerabilities through the first phase.
\begin{tightemize}
\item Work with architecture team to update standard Gradle builds to include Sonar analysis.
\item Prioritize detected issues with Security team.
\item Research and train team leads on mitigation techniques for prioritized items.
\item Work with project planning to schedule mitigation work in monthly time allotments for each team.
\item Track and report progress of initiative to Security team.
\end{tightemize}
\sectionsep

\end{minipage}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Anthony L}{Pane}{ \urlstyle{same}\href{https://www.linkedin.com/in/paneanthony/}{linkedin.com/in/paneanthony}\\
\href{mailto:alpane19@gmail.com}{alpane19@gmail.com} | 631.566.8353
}

\hfill
\begin{minipage}[t]{1.0\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS - Continued
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Recent Projects - Continued}
\runsubsection{User Engagement}
\descript{| Principal Application Architect}
\location{Java, Spring, React, ActiveMQ, SQL | Teams: India, US}
Promote desired user behaviors in order to streamline and improve labor management processes, resulting in higher service quality, employee loyalty and increased business revenues.{ \urlstyle{same}\href{https://www.unifocus.com/newsroom/industry-first-workforce-mgmt-motivation-engagement-with-gamification-capabilities}{Press Release}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Analyzed requirements to create context map and visualize integration points using Domain Driven Design techniques resulting in three new bounded contexts.
\item Review UX designs to determine technical requirements and flow.
\item Analyzed requirement dependencies in order to decompose and prioritize user stories while minimizing bottlenecks. 
\item Work with architecture team to design and implement Domain Event pub/sub infrastructure using the Outbox pattern to support the applications event driven design.
\item Work with architecture and platform team to establish infrastructure, security, and delivery pipeline requirements.
\item Facilitate api and event work required from upstream bounded contexts spread across three additional teams.
\item Pair program and review code for defects and standards.
\end{tightemize}
\sectionsep

\runsubsection{RMS Modularization}
\descript{| Principal Application Architect}
\location{Java, Spring, React | Teams: US, Architecture}
Modularize the UniFocus 1.7 million line legacy application into microservices using Domain Driven Design and microservice design best practices.
\begin{tightemize}
\item Research and procure training material for Domain Driven Design and Microservices.
\item Create and facilitate developer discussion groups to mentor/train the development staff on required techniques.
\item Work with team leads to analyze the legacy schema consisting of 475 tables in order to assign team and bounded context ownership. 
\item Work with team developers to refactor code into 80+ bounded context modules.
\item Work with team developers to establish appropriate aggregate roots to maintain proper transactional boundaries and invariants. 
\end{tightemize}
\sectionsep

\runsubsection{Swing to React Conversion}
\descript{| Principal Application Architect}
\location{Java, React | Teams: US, Croatia, India, Architecture}
Convert legacy Swing UI screens into modularized React applications in order to increase product marketability.
\begin{tightemize}
\item Research and procure training material for TypeScript, React, and Jest.
\item Establish UniFocus coding standards for React/Typescript.
\item Work with architecture on infrastructure and tooling requirements around town planning concerns such as common error handling and reporting, localization, and security.
\item Create and facilitate developer discussion groups to mentor/train the development staff on required techniques.
\item Create wrapper to enable AG-Grid third party tool to meet UniFocus needs for validation, typescript typings, ease of use, look and feel, and support for common grid cell types.
\item Provide technical support for teams during conversion of 80+ screens and communication for any technical nuances/patterns to maintain developer productivity.
\end{tightemize}
\sectionsep

\runsubsection{Time and Attendance}
\descript{| Team Lead, Domain Expert}
\location{Java, React | Teams: US}
Track employee time, reduce labor costs, and maintain compliance to labor laws and union contracts for over 450k employees around the globe.
\begin{tightemize}
\item Responsible for all design and code since inception. 
\item Primary technologies include React, TypeScript, Java, Spring, Hibernate, Spock, SQL
\item Lead team of 3 developers and 1 QA
\item Physical and mobile time clocks with biometric interfaces, punch rules and restrictions.
\item Business rules engine for real time payroll calculations in full compliance with federal, state, corporate and union rules.
\item Time card management, attendance point tracking, benefit accruals, payroll interfaces, tip pooling calculation and distribution, overtime and violations alerting. 
\end{tightemize}
\sectionsep

\end{minipage} 
 
\end{document}  \documentclass[]{article}
